### 2013-09-26 Tex/chapters/results.tex
andere Schreibweise zur Kantenzahl
Fehlerkorrekturen, Formulierung und Positionierung

            K = \frac{2}{N} \sum_{E} 1.

@@

        Where \(E\) is the set of edges.

@@

        the normalization is done using the found power law function.

@@

        Anyway, the degree seems to have a major impact on
        the critical temperature \(T_c\), but it is not a trivial one.

@@

        for the RNG are smaller than those for the GG.

@@

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Middle: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}
                determined power law function over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Note that the \(\sigma = 0\) point of the GG is not displayed.
                The found power law function seems to be a good approximation.
                But at least for the RNG and at least for small values of
                \(\sigma\) on the GG it can not explain everything.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htb]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plot Fig.\ \ref{fig:Tc_J} shows that
        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
            {
                The critical temperature is plotted as a function of the
                average edge weight. T
            }
            \label{fig:Tc_J}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
        that there is no linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        \begin{figure}[hbt]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        Although one could assume, that the course of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        should be strongly influenced by the mean length of the edges, because \(J_{ij}\)
        is a function on the edge length \(d_{ij}\), this is not the case.
        As shown in Fig.\ \ref{fig:TcD}, it shows especially at low \(\sigma\)
        a more complicated course than both \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
        This is a hint that the influence of \(K\) on \(T_c\) is much more
        important than the influence of \(d\) and therefore the influence
        of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).
        \begin{figure}[hbt]
            \centering
            \subfigure[][]
            {
                \label{sfig:TcD:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_d}
            }
            \subfigure[][]
            {
                \label{sfig:TcD:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_d}
            }

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                The mean length of all edges \(d\) for
                \subref{sfig:TcD:RNG} RNG
                and \subref{sfig:TcD:GG} GG for different system sizes \(L\)
                averaged over 100 different realizations.
            }
            \label{fig:TcD}
        \end{figure}\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &\approx \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

>>>>

            K = \frac{2}{N} \# E.

@@

        Where \(\# E\) is the number of edges of the graph.

@@

        the normalization is done using power law function obtained through the fit from Fig.\ \ref{fig:Tc_K}.

@@

@@

        for the RNG are smaller than those for the GG.\\
        Anyway, this analysis shows that the degree has a major impact on
        the critical temperature \(T_c\), but it also shows that there
        have to be other graph properties having a minor influence on \(T_{c}\).

@@

            \caption[Critical Temperature Normalized by Degree of the Graph]
            {
                Top: Degree \(K\) of graph over different
                disorder parameters \(\sigma\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Middle: Critical temperatures normalized by degree over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG.
                Bottom: Critical temperatures normalized by the in Fig.\ \ref{fig:Tc_K}
                determined power law function over different
                disorder parameters for
                \subref{sfig:Tc_norm_deg_fit:RNG} the RNG and
                \subref{sfig:Tc_norm_deg_fit:GG} the GG.
                Note that the \(\sigma = 0\) point of the GG is not displayed.
                The found power law function seems to be a good approximation.
                But at least for the RNG and at least for small values of
                \(\sigma\) on the GG it can not explain everything.
            }
            \label{fig:Tc_deg}
        \end{figure}\\
        To understand the jump of \(T_c\) on a GG it seems to be necessary to
        understand the jump of \(K\), which is easily explained
        by the definition of the GG. As evident from Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
        a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
        To fully understand this, take four nodes forming a square. The edge
        across the diagonal of the plaquette does not exist, because the
        other two nodes are located exactly on the border
        of the lune. Moving one node slightly into the square, causes the lune
        to get smaller, hence no other nodes are inside or on the border of
        the lune anymore and the new diagonal edge appears. This process is sketched in
        Fig.\ \ref{fig:GGEdge}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]{
                \label{sfig:GGEdge:before}
                \input{images/GGEdgeBefore}
            }
            \subfigure[][]{
                \label{sfig:GGEdge:after}
                \input{images/GGEdgeAfter}
            }
            \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
            {
                \subref{sfig:GGEdge:before} The edge across does not exist,
                because the other two nodes are on the edge of the lune.
                \subref{sfig:GGEdge:after} Moving one node slightly into the
                square, causes the lune to get smaller, hence no other nodes
                are inside or on the edge of the lune anymore and the edge
                appears.
            }
            \label{fig:GGEdge}
        \end{figure}\\
        Further, the increase of \(T_c\) on the GG can be made plausible.
        Also, the maximum value of \(K\) and the maximum value of \(T_c\)
        are observed at a similar value of \(\sigma\). Hence, while displacing the nodes, there arise more edges
        than edges are vanishing until \(\sigma \approx 0.15\) is reached.
        Then more edges disappear than appear at further displacement. This
        is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}.
        \begin{figure}[htb]
            \subfigure[][$\sigma = 0.00$]
            {
                \label{sfig:GG_sigma:0.00}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
            }
            \subfigure[][$\sigma = 0.01$]
            {
                \label{sfig:GG_sigma:0.01}
                \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
            }

@@

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J_{ij}\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plot Fig.\ \ref{fig:Tc_J} shows that
        there is a less obvious dependency between \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        than between \(T_c\) and \(K\) (c.f.\ Fig.\ \ref{fig:Tc_K}).
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.45\textwidth]{plots/Tc_J}
            \caption[Critical Temperature as a Function of the Degree of the Graph]
            {
                The critical temperature is plotted as a function of the
                average edge weight. The curve shows a less straight line
                than Fig.\ \ref{fig:Tc_K}.
            }
            \label{fig:Tc_J}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} and Fig.\ \ref{fig:Tc_J} show
        that there is no linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        \begin{figure}[hbtp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \subfigure[][]
            {
                \label{sfig:TcD:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_d}
            }
            \subfigure[][]
            {
                \label{sfig:TcD:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_d}
            }

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Middle: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
                Bottom: The mean length of all edges \(d\) for
                \subref{sfig:TcD:RNG} RNG
                and \subref{sfig:TcD:GG} GG for different system sizes \(L\)
                averaged over 100 different realizations.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        Although one could assume, that the course of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        should be strongly influenced by the mean length of the edges, because \(J_{ij}\)
        is a function on the edge length \(d_{ij}\), this is not the case.
        As shown in Fig.\ \ref{fig:TcJ}\subref{sfig:TcD:RNG}\subref{sfig:TcD:GG}, it shows especially at low \(\sigma\)
        a more complicated course than both \(T_c\) and \(\avg{\sum_{\avg{i,j}} J_{ij}}\).
        This is a hint that the influence of \(K\) on \(T_c\) is much more
        important than the influence of \(d\) and therefore the influence
        of \(J_{i,j}\) on \(T_c\). At least with the chosen function for \(J_{ij}\).
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &\approx \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).
